---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Group.Means

<!-- badges: start -->
<!-- badges: end -->

The goal of Group.Means is to calculate the mean of a variable of specified groups

## Files in this repo
There are folders for the R file, Man file, and tests to run with this package. There are also License files for this package, documentation of the package requirements/other details, and namespace files in the main repository. You can also find the rmd where the files were created titled "Grouped.Means.Rmd".


## Installation

You can install the development version of Group.Means by accessing the online repository like so:

```{r}
library(devtools)
devtools::install_github("stat545ubc-2024/Grouped-Means")

```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(Group.Means)
library(gapminder)
#Finding the average life expectancy by country in the gapminder dataset
answer1.0 <-group_mean(gapminder, country, lifeExp)
print(answer1.0)
```

